Vulnerability Analysis of Container Images in Neuroimaging

### 2020-07-13 paper.tex
fixed databases

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{array}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[flushleft]{threeparttable}

@@

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}

@@

\todo{Add related work on vulnerability scanning}

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources. The Figure~\ref{anchore} displays a list of all sources
that it refers at the time of this study.

%for instance, Ubuntu launchpad database to get
%vulnerability data related to Ubuntu 
\tristan{You need to be accurate on these sources, this is not ``for instance". 
You should list all the sources used in the experiments, for all image types: Ubuntu but also CentOS, Debian, Alpine.}.

\begin{figure*}[!ht]
    \centering
	\begin{subfigure}[t]{0.3\textwidth}
        \includegraphics[height=2.0in]{Figures/anchore.png}
        \caption{Anchore}
        \label{anchore}
    \end{subfigure}%
    ~ 
	\begin{subfigure}[t]{0.3\textwidth}
        \includegraphics[height=2.5in]{Figures/vuls.png}
        \caption{Vuls}
        \label{vuls}
    \end{subfigure}
     ~
	\begin{subfigure}[t]{0.3\textwidth}
        \includegraphics[height=2.0in]{Figures/clair.png}
        \caption{Clair}
	\label{clair}
    \end{subfigure}
    \caption{Vulnerability databases used by scanners}
    \label{database}
\end{figure*}

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager
in the image through SSH. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources, which are listed in Figure~\ref{vuls}.
%from the Open Vulnerability
%and Assessment Language (OVAL) database 
\tristan{Does it contain
vulnerabilities for all distributions?} 
\tristan{The Vuls website says that it uses multiple vulnerability databases: https://vuls.io/docs/en/main-features.html Are you sure 
that you only used OVAL and if so, why?}. According to this list, Vuls
refers to OVAL database for some distribution e.g. Ubuntu, Debian, etc.
It is worth noting that there is
no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair-scanner scans the image,
prepares the list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist.
In our experiments, we did not use a whitelist to filter scanning results in
order to make a fair comparison between scanners.
\tristan{What is this whitelist about, and which one did you use?}. Clair
scanner maintains a Docker image with the up-to-date vulnerability
database from a set of different sources listed in Figure~\ref{clair}.  \tristan{Please mention the vulnerability sources for all distributions}.
 We use Clair-scanner version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

Singularity Tools (Stools)
are an extension of Clair scanner for Singularity images. Stools
exports Singularity image to \url{tar.gz} format, masquerading as a single layer docker image
to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we use Singularity Tools version 3.2.1 through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}, which is using another Docker
image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
We follow the steps mentioned in
\href{https://github.com/singularityhub/stools}{Stools Github} to scan
Singularity images. \tristan{which docker images did you use for clair and clair database?}

@@

\tristan{This section is still very confusing. I can rewrite it but would first need to
have a clear picture of vulnerability statuses across the tested Linux distributions. 
Are vulnerability statuses present only in Ubuntu, or are there statuses in other distributions too?
If so, what are the vulnerability statuses in the other distributions?
}
BIDS app and Boutiques images in our experiments have diverse Linux
distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
distribution has different releases in general. Regarding Ubuntu, it has different
types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
differently depending on the different Ubuntu release types. It is 
important to provide an overview of these Ubuntu releases types, 
since Ubuntu is heavily utilized in our experiments. 
\todo{Explain the situation with centos, update figure 3 accordingly.}
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

@@

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, which is a open-source tool that
helps scientists to make their research reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
\tristan{How did you run the applications? Which command lines, why, etc}. Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process \tristan{Can we please have at least a README for these scripts?}, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

@@

\begin{table*}[!ht]
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} & {Anchore} & {Clair} & {Vuls} &{Stools}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{fullresults.csv}{}{\csvlinetotablerow}%
       \centering
        \caption{\label{table1}Number of vulnerabilities by scanners}
\end{table*}

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
      \end{figure*}

\begin{figure}[!ht]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

@@

Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This figure excludes Centos Docker images because scanners report results in different
formats for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
to report pending patches that need to be applied to specific packages
,whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
vulnerabilities in packages. Also, we excluded two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/afni\_proc} from this figure, since we do not have Vuls scanning results for these images. 
\tristan{According to our discussion, this is only for Ubuntu. This should be clarified.}

@@

\begin{figure*}[!ht]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Number of vulnerabilities before and
        after update of the images}
      \end{figure*}

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair-scanner but they affect Ubuntu 14.04 LTS, and hence detected by Vuls. The CVE-2017-1375 is an example
of such vulnerabilities.

\textbf{False negatives:} False negative reporting is detected. Clair-scanner and Vuls
are missing vulnerabilities that they should have detected. For example, the CVE-2016-9082 
is present in package Cairo in Xenial release and it is not detected by Clair-scanner.
Vuls is also missing vulnerabilities such as CVE-2019-5094.

\textbf{False positives:} False positive reporting is also detected. For instance,
there are false positives in clair-scanner.
Some vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image, however, Clair-scanner have reported such vulnerabilities.
For instance, CVE-2019-1274 is an example of such vulnerabilities. 
%is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
%Clair is only referring to Ubuntu 14.04 ESM release. 
The reasons of Clair showing
false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}

>>>>

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{array}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage{anyfontsize}
\usepackage[flushleft]{threeparttable}

@@

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}
\begin{filecontents*}{resul.csv}
labels,names,A,C,V,Stools
a,bids/example,838,663,683,
b,bids/freesurfer,353,215,192,
c,bids/ndmg,934,757,782,
d,\textcolor{red}{bids/broccoli:v1.0.0},79,79,117,
e,bids/fibredensityandcrosssection,1086,849,868,
f,bids/spm,191,246,235,
g,poldracklab/mriqc:0.15.0,432,328,332,
h,bids/cpac:v1.0.1a\_22,698,524,535,
I,bids/hyperalignment,1717,1327,1433,
j,bids/mindboggle:0.0.4-1,671,955,569,
k,bids/mrtrix3\_connectome,275,157,158,
l,bids/rs\_signal\_extract:0.1,867,454,473,
m,bids/aa:v0.2.0,189,244,233,
n,bids/niak,1482,1366,1420,
o,bids/oppni:v0.7.0-1,913,698,723,
p,poldracklab/fmriprep:unstable,516,355,393,
q,bids/brainiak-srm,897,484,503,
r,bids/nipypelines:0.3.0,641,878,451,
s,bids/hcppipelines:v3.17.0-18,526,873,620,
t,bids/magetbrain,112,117,126,
u,bids/tracula:v6.0.0-4,874,664,683,
v,bids/baracus,172,238,216,
w,bids/antscorticalthickness:v2.2.0-1,289,27,no oval data,
x,bids/dparsf:v4.3.12,507,750,757,
y,bids/afni\_proc,67,16,no oval data,
z,bids/rshrf:1.0.1,5,3,3,
aa,bids/ndmg:v0.1.0,934,758,782,
ab,\textcolor{red}{mcin/qeeg:latest},46,46,142,
ac,\textcolor{red}{camarasu/creaphase:0.3},54,54,186,
ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest},70,76,157,
ae,\textcolor{red}{mcin/docker-fsl:latest},75,75,201,
af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest},70,76,157,
ah,\textcolor{red}{bt5e/ants:latest},150,156,336,
ai,poldracklab/fmriprep:1.2.3,591,441,447,
aj,gkiar/dwipreproc\_fsl-5.0.11\_minified,391,258,263,
ak,gkiar/mask2boundary:v0.1.0,15,11,11,
al,\textcolor{red}{mcin/ica-aroma:latest},75,75,202,
am,c3genomics/genpipes,,,,99
an,bioinformatics-group/aqua-singularity-recipe,,,,7
ao,MontrealSergiy/BEst,,,,106
ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
aq,shots47s/bids-freesurfer-6.0,,,,212
ar,shots47s/bids-fmriprep-1.2.3,,,,453
\end{filecontents*}

@@

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources. The Table~\ref{database} displays a list of all sources
that it refers at the time of this study.

%for instance, Ubuntu launchpad database to get
%vulnerability data related to Ubuntu

%\begin{figure*}[!ht]
%    \centering
%	\begin{subfigure}[t]{0.3\textwidth}
%        \includegraphics[height=2.0in]{Figures/anchore.png}
%        \caption{Anchore}
%        \label{anchore}
%    \end{subfigure}%
%    ~ 
%	\begin{subfigure}[t]{0.3\textwidth}
%        \includegraphics[height=2.5in]{Figures/vuls.png}
%        \caption{Vuls}
%        \label{vuls}
%    \end{subfigure}
%     ~
%	\begin{subfigure}[t]{0.3\textwidth}
%        \includegraphics[height=2.0in]{Figures/clair.png}
%        \caption{Clair}
%	\label{clair}
%    \end{subfigure}
%    \caption{Vulnerability databases used by scanners}
%    \label{database}
%\end{figure*}
\begin{figure*}
\begin{tabular}{ |c|c|c|c| }
 \hline
\textbf{OS} &	\textbf{Anchore} &	\textbf{Vuls} &	\textbf{Clair} \\
\hline
	\textbf{Alpine} & Alpine-SecDB &	Alpine-SecDB &	Alpine-SecDB \\
\hline
	\textbf{CentOS} & Red Hat Enterprise Linux Oval & Red Hat Enterprise Linux OVAL And Red Hat Security Advisories & Red Hat Security Data \\
\hline
	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL and Debian Security Bug Tracker & Debian Security Bug Tracker \\
\hline
	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL &	Ubuntu CVE Tracker \\
 \hline
\end{tabular}
\caption{Vulnerability databases used by scanners for different OS distributions}
\label{database}
\end{figure*}

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager
in the image through SSH. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources, which are listed in the Table~\ref{database}.
%from the Open Vulnerability
%and Assessment Language (OVAL) database 
According to this list, Vuls
refers to OVAL database for some distribution e.g. Ubuntu, Debian, etc.
It is worth noting that there is
no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair-scanner scans the image,
prepares the list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist.
In our experiments, we did not use a whitelist to filter scanning results in
order to make a fair comparison between scanners.
Clair scanner maintains a Docker image with the up-to-date vulnerability
database from a set of different sources listed in the Table~\ref{database}.
We use Clair-scanner version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

Singularity Tools (Stools)
are an extension of Clair scanner for Singularity images. Stools
exports Singularity image to \texttt{tar.gz} format, masquerading as a single layer docker image
to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we use Singularity Tools version 3.2.1 through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}, which is using another Docker
image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
We follow the steps mentioned in
\href{https://github.com/singularityhub/stools}{Stools Github} to scan
Singularity images.

@@

BIDS app and Boutiques images in our experiments have diverse Linux
distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
distribution has different releases in general. Regarding Ubuntu, it has different
types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
differently depending on the different Ubuntu release types. It is 
important to provide an overview of these Ubuntu releases types, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

@@

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, which is a open-source tool that
helps scientists to make their research reproducible. This tool traces operating system calls used by the
application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

@@

%\csvreader[tabular=|l|l|l|l|l|l|,
%         table head=\hline \textbf{ First Name} & \textbf{Last Nmae} & {a} & {b} & {c} & {d}\\\hline,
%     late after line = \\\hline]%
% {resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
%         {\labels & \names & \A & \C & \V & \Stools}%
%

\begin{table*}[!ht]
\csvreader[%
 %respect all,%
 % before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
  %    \begin{adjustbox}{max width=\textwidth},
  %after reading=\end{adjustbox},
 tabular={|c|c|c|c|c|c|},
	table head = \hline\textbf{Image Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
	late after line= \\,
        late after last line=\\\hline %
	]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
        {\labels & \names & \A & \C & \V & \Stools}
       \centering
	\vspace*{1mm}
	\caption{\label{table1}Number of vulnerabilities by scanners (all Centos images are highlighted)} 
\end{table*}

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/vulngraph.pdf}}
	\vspace*{-7mm}
        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
      \end{figure*}

\begin{figure}[!ht]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
	\vspace*{-10mm}
	\caption{\label{fig:venn} Scanner results (excluding non-comparable image results)}
\end{figure}

@@

Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This Figure excludes Centos Docker images (highlighted images in Table\~ref{table1}) because scanners report results in different
formats for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
to report pending patches that need to be applied to specific packages,
whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
vulnerabilities in packages. Also, we excluded two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/afni\_proc} from this figure, since we do not have Vuls scanning results for these images.

@@

\begin{figure*}[!ht]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
	\vspace*{-7mm}
        \caption{\label{fig:graph2} Number of vulnerabilities before and
        after update of the images}
      \end{figure*}

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
	\vspace*{-5mm}
        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair-scanner but they affect Ubuntu 14.04 LTS, and hence detected by Vuls. The CVE-2017-1375 is an example
of such vulnerabilities.

\textbf{Misses:} Clair-scanner and Vuls
are missing vulnerabilities that they should have detected. For example, the CVE-2016-9082 
is present in package Cairo in Xenial release and it is not detected by Clair-scanner.
Vuls is also missing vulnerabilities such as CVE-2019-5094.

\textbf{Wrong Detections:} 
Some vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image, however, Clair have reported such vulnerabilities.
For instance, CVE-2019-1274 is an example of such vulnerabilities. 
%is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
%Clair is only referring to Ubuntu 14.04 ESM release. 
We reported this issue on two Google groups of Clair i.e CoreOS Dev and
clair-dev \url{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
